\documentclass[11pt,a4paper]{article}

\usepackage[english]{babel}
\usepackage{pdflscape}
\usepackage{pgfgantt}
\usepackage{tikz}

\begin{document}

\title{Roadmap}
\author{Martin Gwerder}
\date{Dezemer 2013}
\maketitle

\section{Abstract}
The following document offers an outline of the Roadmap. All positions of the Roadmap have been described. For the Glossar of this document please refer to the thesis document.

\section{Structure of the Thesis}
The thesis shall be structured in four main Parts:

\begin{itemize}
	\item Information Gathering\\
	      In this phase there should be intense research on existing technologies, standards, ground Theory and researches relating to the topic. The findings should be collected and consolidated.
	\item Analysis\\
				The information found needs to be consolidated analyzed for their usefulness and outlining gaps in the current technology.
	\item Design\\
				The analyzed information needs to be consolidated and recombined into a target solution. The proposed solution should be ready to be defined in an RFC-Document.
	\item Writing of the RFC-Document\\
				Based on the proposed design an RFC-Document should be written. This document must reflect a minimum and a recommended baseline for an anonymous mail infrastructure.
	\item Implementation\\
				Based on the RFC-Document there should be a client implementation and a server implementation for an minimum baseline client.
\end{itemize}
\begin{landscape}
\section{Gantt chart}
\resizebox{\textwidth}{0.95\textheight}{
\begin{ganttchart}[vgrid,hgrid]{1}{40}
\gantttitle{2013}{1} \gantttitle{2014}{12} \gantttitle{2015}{12}  \gantttitle{2016}{12} \gantttitle{2017}{3}\\
\gantttitlelist{12}{1}\gantttitlelist{1,...,12}{1}\gantttitlelist{1,...,12}{1}\gantttitlelist{1,...,12}{1}\gantttitlelist{1,...,3}{1} \\
%\gantttitlecalendar{year, month} \\
\ganttgroup{Ground work}{1}{17} \\
\ganttbar{Initialisation}{1}{4}\\
\ganttbar{Info gathering}{1}{8}\\
\ganttbar{Analysis}{1}{12}\\
\ganttlinkedbar{Design}{13}{17}\\
\ganttgroup{POC}{18}{36} \\
\ganttbar{RFC}{18}{23}\\
\ganttlinkedmilestone{RFC to IETF}{23}\\
\ganttlinkedbar{Implementation}{24}{36}\\
\ganttlinkedbar{Finalization}{37}{40}\\
%\ganttlink{elem6}{elem7}
\ganttlink{elem4}{elem6}
\ganttlink{elem2}{elem4}
%\ganttbar{Task 1}{1}{2} \\
%\ganttlinkedbar{Task 2}{3}{7}
%\ganttnewline\ganttmilestone{Milestone}{7}
%\ganttnewline\ganttbar{Final Task}{8}{12}
%\ganttlink{elem2}{elem3}
%\ganttlink{elem3}{elem4}
\end{ganttchart}
}
\end{landscape}
\end{document}

