\chapter{Designing an approach}
\section{Defining system boundaries}
\subsection{Thread model}
As an adverser we assume the following attributes:
\begin{itemize}
\item Available founding is huge.
\item Can have own mailer infrastructure.
\item Is able to read, write or modify network data freely at any point of the net.
\end{itemize}
His intensions are:
\begin{itemize}
\item Discover message flows
\item Discover message contents
\item Identify users of the system
\end{itemize}

\subsection{User model}
The assumed user of the system is:
\begin{itemize}
\item Does care about privacy.
\item Has no special computer knowhow.
\item Has the ability to install a program or plugin.
\item Has no cryptographic knowhow.
\item Is using a device with enough calculation power to solve cryptographic tasks.
\end{itemize}
His intensions are:
\begin{itemize}
\item Send personal or confidential Information securely to another user
\end{itemize}
His expectations are:
\begin{itemize}
\item System should be easy to configure and maintain (in an ideal world: Zero touch). 
\item System should be fast.
\item System should be reliable.
\item System should work on any client he is using.
\item System should not be a legal problem to him or any of his peers.
\end{itemize}

\subsection{Mail server admin model}
The assumed mail server admin of the system is:
\begin{itemize}
\item Does care about privacy.
\item Has considerable computer knowhow.
\item Has the ability to install a program or plugin.
\item Has possibly no cryptographic knowhow.
\item Does know his own mail infrastructure.
\item Is using a device with enough calculation power to solve cryptographic tasks.
\end{itemize}
His intensions are:
\begin{itemize}
\item Support his users in sending personal or confidential information securely to another user
\end{itemize}
His expectations are:
\begin{itemize}
\item System should be easy to configure and maintain (in an ideal world: Zero touch). 
\item System should be fast.
\item System should be reliable.
\item System should work on any client he is using.
\item System should not be a legal problem for him or his company.
\item System should still allow him to do regulatory tasks such as virus scanning or backup.
\end{itemize}

\section{Basic Requirements of an approach}

\chapter{Specifying a target solution}
\section{Blocks}
\subsection{Preamble}
\begin{itemize}
  \item identity
  \item Request Number (RNR)
  \item Identity signature
  \item Message key
  \item Shuffle
\end{itemize}

\subsection{Routing block}
\begin{itemize}
  \item Next hop address
  \item RNR (must match preamble)
  \item Validity time
  \item delivery expiry
  \item Message checksum (optional)
  \item Padding  (optional)
\end{itemize}

\subsection{Address request block}

\section{Messages}
\subsection{Basecom}
\begin{itemize}
  \item Request Server keys
  \item Request identity (identity and key tuple)
  \item Request size quota (size in bytes and end time)
  \item Request Puzzle spec
  \item Request capabilities
\end{itemize}
